The five pillars of computational reproducibility: Bioinformatics and beyond

### 2023-06-02 manuscript/5pillars.Rmd
Close #3
ack

@@

Source: https://github.com/markziemann/5pillars/blob/main/manuscript/5pillars.Rmd

@@

We are grateful to individuals who provided feedback on an earlier draft of the concept including
Dr Aziz Khan (Stanford University),
Dr Sriganesh Srihari (QIMR Berghofer Medical Research Institute),
Dr Barbara Zdrazil (EMBL-EBI) and
Dr Irene López Santiago (EMBL-EBI).

>>>>

<details><summary>Author information (*click to expand*)</summary><p>

@@

| Author | ORCID |
| --- | --- |
| Mark Ziemann | 0000-0002-7688-6974 |
| Samuel S. Minot | 0000-0003-1639-3905 |
| Pierre Poulain | 0000-0003-4177-3619 |
| Anusuiya Bora | 0009-0006-2908-1352 |

</details>
</p>
Source: https://github.com/markziemann/5pillars/blob/main/manuscript/5pillars.Rmd

@@

We are grateful to individuals who provided feedback on an earlier draft of the concept including
Dr Aziz Khan (Stanford University),
Dr Sriganesh Srihari (QIMR Berghofer Medical Research Institute),
Dr Barbara Zdrazil (EMBL-EBI) and
Dr Irene López Santiago (EMBL-EBI).
Special thanks to Dr Altuna Akalin (Max Delbrück Center, Germany) and
Dr Simon Tournier (Paris Cité University, France) for advice on Guix.
